What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-02-01 text/01_CogSci_abstract/paper.tex
more edits everywhere

On \emph{paired comparison} (PC) trials, participants saw an item's context sentence and had to
click on one of two options shown side by side -- whichever one they thought was more likely.
Each option used the appropriate PC frame in\tableref{tab:Items} and numbers were filled in by
comparing the following bins: 1 vs 2, 2 vs 6, 6 vs 11, 11 vs 14, and 14 vs 15. Paired
comparison trials always occurred as a block of five trials, with order of comparisons
randomized within block.

@@

Finally, consider the link function for \textbf{bin comparisons}. We are interested in the
likelihood with which participant $i$ selects the higher bin for item $j$ in bin comparison
condition $l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. The
perhaps most natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to
the difference between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, this does not
appear to be what participants were doing. Indeed, a model that implements this idea blatantly
fails to capture the relevant regularities in the data. Another plausible link function is to
assume that what matters is the distance to the mode of $P_{ij}$: soft-max prefer the bin that
is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from the
prototype.\footnote{$(1 + \exp(2b(1-x)) )^{-1} = \frac{\exp(b x)}{\exp(b
    x) + \exp(b y)}$
  if $x = 2 - y$.}
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

@@

Means and bounds of 95\% HDIs of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, participants had no
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
participants, on average, had a strong tendency to choose modal in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \midrule
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
\end{tabular}
\caption{Summary statistics for posteriors on parameters}
\label{tab:SummaryStats}
\end{table}

@@

Future research should investigate whether and how our results can be extended to other types
of uncertain variables. Here, guided by the needs of many previous Bayesian cognitive models,
we focused on uncertainty about unidimensional contiguous variables. It remains to be seen
whether the binned histogram task can be applied to higher-dimensional variables, like joint
prior beliefs over, say, \emph{height} and \emph{weight} of an individual or, more abstractly,
different dimensions of a multi-dimensional property like \emph{intelligence}. Another
challenge lies in devising means of eliciting prior expectations about properties that do not
have clear and familiar measure terms, like the mentioned \emph{intelligence}.

>>>>

On \emph{paired comparison} (PC) trials, participants saw an item's context sentence and had to
click on one of two options shown side by side -- whichever one they thought was more likely.
Each option used the appropriate PC frame in \tableref{tab:Items} and numbers were filled in by
comparing the following bins: 1 vs 2, 2 vs 6, 6 vs 11, 11 vs 14, and 14 vs 15. Paired
comparison trials always occurred as a block of five trials, with order of comparisons
randomized within block.

@@

Finally, consider the link function for \textbf{bin comparisons}. We are interested in the
likelihood with which participant $i$ selects the higher bin for item $j$ in bin comparison
condition $l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. 
Perhaps the most natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to
the difference between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, this does not
appear to be what participants were doing. Indeed, a model that implements this idea blatantly
fails to capture the relevant regularities in the data. Another plausible link function is to
assume that what matters is the distance to the mode of $P_{ij}$: soft-max prefer the bin that
is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from the
prototype.\footnote{$(1 + \exp(2b(1-x)) )^{-1} = \frac{\exp(b x)}{\exp(b
    x) + \exp(b y)}$
  if $x = 2 - y$.}
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

@@

Means and bounds of 95\% high-density intervals (HDIs) of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, participants had no
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
participants, on average, had a strong tendency to choose modal values in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \midrule
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
\end{tabular}
\caption{Summary statistics for posteriors on parameters}
\label{tab:SummaryStats}
\end{table}

@@

Future research should investigate whether and how our results can be extended to other types
of uncertain variables. Here, guided by the needs of many previous Bayesian cognitive models,
we focused on uncertainty about unidimensional contiguous variables. It remains to be seen
whether the binned histogram task can be applied to higher-dimensional variables, like joint
prior beliefs over, say, \emph{height} and \emph{weight} of an individual or, more abstractly,
different dimensions of a multi-dimensional property like \emph{intelligence}. Another
challenge lies in devising means of eliciting prior expectations about properties that do not
have clear and familiar measure terms that can be used to label bins---again like \emph{intelligence}.
